---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prisoners

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/prisoners)](https://CRAN.R-project.org/package=prisoners)
<!-- badges: end -->

The goal of prisoners is to provide functinoality to simulate the 100 prisoners problem (https://en.wikipedia.org/wiki/100_prisoners_problem)

## Installation

You can install the development version of prisoners from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ndphillips/prisoners")
```

## Example

```{r example}
library(prisoners)
```

### Simulate Prisoner Games

Simulate multiple teams of prisoners using `prisoners_simulate()`

```{r, results = "hide", message = FALSE}
set.seed(123)

# Simulate 100 teams of 100 prisoners using the 'agent' method
result_agent <- prisoners_simulate(
  teams_n = 100,
  prisoners_n = 100,
  pick_max = 50,
  method = "environment"
)
```

```{r}
# Print the result
result_agent
```

Access key results using `pull_*()` functions:

```{r}
# What were the key outcomes for each team?
pull_outcomes(result_agent)

# What was the overall success rate?
pull_success_p(result_agent)

# How long did the simulation take?
pull_duration_mean(result_agent)
```

Visualise the results using `plot_*()` functions:

```{r}
plot_boxes_max(result_agent)
```

### Helpers

Create your own rooms using `create_rooms()`

```{r}
# Create 10 rooms of 100 boxes
boxes_ls <- create_rooms(rooms_n = 10, boxes_n = 100)
```
