---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# prisoners

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/prisoners)](https://CRAN.R-project.org/package=prisoners)
<!-- badges: end -->

The goal of prisoners is to provide functinoality to simulate the 100 prisoners problem (https://en.wikipedia.org/wiki/100_prisoners_problem) as stated below:

>The director of a prison offers 100 death row prisoners, who are numbered from 1 to 100, a last chance. A room contains a cupboard with 100 drawers. The director randomly puts one prisoner's number in each closed drawer. The prisoners enter the room, one after another. Each prisoner may open and look into 50 drawers in any order. The drawers are closed again afterwards. If, during this search, every prisoner finds their number in one of the drawers, all prisoners are pardoned. If even one prisoner does not find their number, all prisoners die. Before the first prisoner enters the room, the prisoners may discuss strategy — but may not communicate once the first prisoner enters to look in the drawers. What is the prisoners' best strategy?

Learn more about why I created this package at my blog post [here](https://ndphillips.github.io/posts/the_prisoners.html).

## Installation

You can install the development version of prisoners from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ndphillips/prisoners")
```

## Example

```{r example}
library(prisoners)
```

### Simulate Prisoner Games

Simulate multiple teams of prisoners using `prisoners_simulate()`.

Below, I'll simulate a prisoner game with the following arguments:

- `teams_n = 100`: 100 teams of prisoners
- `prisoners_n = 100`: 100 prisoners in each team
- `open_max = 50`: 50 maximum number of boxes each prisoner can open

```{r, results = "hide", message = FALSE}
set.seed(12345)

# Simulate 100 teams of 100 prisoners using the 'agent' method
result <- prisoners_simulate(
  rooms = create_rooms(
    rooms_n = 100,
    prisoners_n = 100
  ),
  open_max = 50 # Maximum number of boxes each prisoner can open
)
```

```{r}
# Print the result
result
```

Access key results using `pull_*()` functions:

```{r}
# What were the key outcomes for each team?
pull_outcomes(result)

# What was the overall success rate?
pull_success_p(result)

# How long did the simulation take?
pull_duration_mean(result)
```

Visualise the results using `plot_*()` functions:

```{r}
plot_boxes_max(result)
```

### Other Functions

You can create your own rooms using `create_rooms()` and then access individual rooms with `pull_room()` 

```{r}
# Create 10 rooms of 100 boxes
rooms <- create_rooms(
  rooms_n = 10,
  prisoners_n = 100
)

# Pull out the first room
room_1 <- rooms |> 
  pull_room(1)

room_1
```

Given a room, you can add columns indicating loops using `add_loops_to_room()`

```{r}
# Add loops to the room
room_1 <- room_1 |>
  add_loops_to_room()

room_1
```

You can vizualize a room using `plot_room()` (Use `show_loops = FALSE` to show the room without organizing by loops)

```{r, fig.width = 7, fig.height = 7}
# Vizualize a room
room_1 |>
  plot_room()
```
